Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-11-16 docs/ms_sageAbundance.Rmd
adds in Eric's comments

#### Climate covariates
Our approach is based on modeling how changes in plant populations relate to climate variables.
We downloaded daily historic weather data for our study site from the NASA Daymet data set (*available online*)[^link].
The Daymet weather data are interpolated between coarse observation units and captures some spatial variation.
We relied on weather data for the centroid of our study area.
We calculated five climate variables from the Daymet data for the time period coinciding with our remotely sensed data (1984 to 2011).

@@

All parameters in our model converged on stable posterior distributions (Appendix C).
Only the *lagPpt* climate covariate can be considered important based on a 90% credible interval, and it had a positive effect on sagebrush annual percent cover change (Fig. 3).
The posterior mean for the spatial random effect, $\boldsymbol{\eta}$, captured the overall spatial structure of the observed data (Fig. D1).
This indicates our choice of knot placement and dimension reduction strategy was adequate for describing permanent spatial variation in the data.

@@

Discussion
-----------
Landscape-scale population models for plant species have been elusive and challenging to implement [@Schurr2012a; @Merow2014].
Yet, the need to forecast population responses to climate change over large spatial extents is clear, as demonstrated by the wide application of species distribution models [see @Clark2014].
We introduced a new statistical approach to modeling plant populations that overcomes two major hurdles for spatially-explicit population models.
First, we used high resolution species-specific remote sensing data as a response variable.
Thus, we had a spatially-continuous data product of sagebrush abundance over a large spatial extent, meaning we could fit a model at the same spatial resolution and extent as the data. 
In so doing we, overcame a major limitation of most population models that are fit using detailed data from a single location.
Second, borrowing from new methods in spatio-temporal modeling of animal abundance [e.g., @Conn2015], we employed a dimension reduction strategy that rigorously accounted for spatial autocorrelation while also allowing for feasible computational time in model fitting.
Accounting for spatial autocorrelation in this large dataset allows for statistically rigorous inference on the effects of interannual climate on sagebrush cover change in our study region. 
The spatial covariance structure also provided a way to obtain spatially-explicit predictions at a resolution below that of the climate covariates (i.e. within the study region; Figs. 4,5).

>>>>

#### Climate covariates
Our approach is based on modeling how interannual changes in plant cover relate to seasonal climate variables.
We downloaded daily historic weather data for our study site from the NASA Daymet data set (*available online*)[^link].
The Daymet weather data are interpolated between coarse observation units and captures some spatial variation.
We relied on weather data for the centroid of our study area.
We calculated five climate variables from the Daymet data for the time period coinciding with our remotely sensed data (1984 to 2011).

@@

All parameters in our model converged on stable posterior distributions (Appendix C).
Only the *lagPpt* climate covariate can be considered important based on a 90% credible interval, and it had a positive effect on sagebrush percent cover change from year-to-year (Fig. 3).
The posterior mean for the spatial random effect, $\boldsymbol{\eta}$, captured the overall spatial structure of the observed data (Fig. D1).
This indicates our choice of knot placement and dimension reduction strategy was adequate for describing permanent spatial variation in the data.

@@

Discussion
-----------
Landscape-scale population models for plant species have been elusive and challenging to implement [@Schurr2012a; @Merow2014].
Yet, the need to forecast population responses to climate change over large spatial extents is clear, as demonstrated by the wide application of species distribution models [see @Clark2014].
We introduced a new statistical approach to modeling plant populations that overcomes two major hurdles for spatially-explicit population models.
First, we used high resolution species-specific remote sensing data as a response variable.
Thus, we had a spatially-continuous data product of sagebrush abundance over a large spatial extent, meaning we could fit a model at the same spatial resolution and extent as the data. 
In so doing we, overcame a major limitation of most population models that are fit using detailed data from a single location.
Second, borrowing from new methods in spatio-temporal modeling of animal abundance [e.g., @Conn2015], we employed a dimension reduction strategy that accounted for spatial autocorrelation while also allowing for feasible computational time in model fitting.
Accounting for spatial autocorrelation in this large dataset allows for statistically rigorous inference on the effects of interannual climate on sagebrush cover change in our study region. 
The spatial covariance structure also provided a way to obtain spatially-explicit predictions at a resolution below that of the climate covariates (i.e. within the study region; Figs. 4,5).
